Tomographic galaxy clustering with the Subaru Hyper Suprime-Cam first year public data release

### 2019-10-20 doc/Paper/main.tex

We have also investigated the impact of a secondary mode in the redshift distribution for the first tomographic bin. This secondary peak contains 5\% of galaxies and peaks around $z\sim 2.5$ (hence cannot be seen in Figure \ref{fig:nzs}). To investigate the impact of this mode, we manually excise it from redshift distribution and calculate the resulting change in $\Delta \chi^2\sim 0.1$. This indicates that the effect of this bump is to small to be statistically significant. We therefore do not need to worry whether it is real or an artifact of photometric redshift inference.  \as{Fix numbers once Sarah gets back}

>>>>

We have also investigated the impact of a secondary mode in the redshift distribution for the first tomographic bin. This secondary peak contains $\sim$5\% of galaxies and peaks around $z\sim 3$ (hence cannot be seen in Figure \ref{fig:nzs}). To investigate the impact of this mode, we manually excise it from redshift distribution and calculate the resulting change in $\Delta \chi^2\sim 0.05$. This indicates that the effect of this bump is to small to be statistically significant. We therefore do not need to worry whether it is real or an artifact of photometric redshift inference.
